### 2019-09-04 manuscript/manuscript.tex
updated plots, new R analysis of Bergland data

@@

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-cross-validation-binsize.pdf}

  \caption{}
  \label{suppfig:barghi-cross-validation-binsize}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[]{figures/barghi-tailprobs-seqid-0.20.pdf}

  \caption{}
  \label{suppfig:barghi-tailprobs-seqid}
\end{figure}

\subsection{\textcite{Bergland2014-ij} Re-Analysis}

We also applied our temporal covariance approach to \texcite{Bergland2014-ij},
a study that finds evidence of genome-wide fluctuating selection between Spring
and Fall seasons across three years. As described in \textcite{Buffalo2019-io},
we would expect positive covariances between like seasons (i.e. Spring 2010 and
Spring 2011), negative covariances between dislike seasons (i.e. Spring 2010
and Fall 2011) when fluctuating selection is strong and acts genome-wide, as
the original study found. However, while we find temporal covariances that are
non-zero, we find only weak support for a seasonal fluctuating model driving
these covariances. In Supplementary Figure XXX, we show the temporal
covariances from varying reference generations, across Spring/Fall,
Spring/Spring, and Fall/Fall pairs. The first row of temporal covariance matrix
is consistent with fluctuating selection operating for two timepoints, as the
first covariance is negative, and the second is positive, and later covariances
are not statistically differentiable from zero (which could occur if LD and
additive genetic variance decay). However, the all other temporal covariances
do not fit the pattern we would expect under genome-wide fluctuating selection.

We were concerned that this might be due to a flaw in our methods. To address
this concern, we first ensured that our temporal-covariance matrix bias
correction was working as expected. We find that it corrects the relationship
between depth and both variance and covariance (Supplementary Figure XXX) as
expected. We decided to re-analyze the data of \parencite{Bergland2014-ij}
using the same seasonal fluctuating model as the original paper. This model is
a Binomial logit-linked GLM, where the seasons are regressed on the frequency
data, and the binomial weights are determined by the effective number of
chromosomes, $N_{eff} = (2 n_t d_t - 1) / (2 n_t + d_t)$ where, using our
notation, $n_t$ and $d_t$ are the number of diploid individuals and the read
depth at timepoint $t$, respectively. We fit this model on all loci marked as
used in the \textcite{Bergland2014-ij} study. Overall, our p-values for the
Wald test for each locus closely match those of the original paper (Pearson
correlation coefficient 0.98, p-value < $2.2 \times 10^{-16}; see Supplementary
Figure XXX), and the histograms of the p-values are identical (Supplementary
Figure XXX).

While \textcite{Bergland2014-ij} find significant p-values after a Benjamini
and Hochberg FDR p-value adjustment \parencite{Benjamini1995-jy}, they do not
construct a null distribution of p-values as would be expected if fluctuating
selection were not acting, which they could compare their observed p-value
distribution to. Without such a distribution, we cannot know whether we might
expect many variants across the genome to have frequencies that spuriously fit
the pattern of fluctuating seasons. We created this empirical null distribution
by randomly permuting the season labels and re-running the seasonal GLM model.
We find, regardless of whether we permute at the locus-level or the permutation
replicate-level, that the observed seasonal p-value distribution
\textcite{Bergland2014-ij} is not enriched for significant p-values beyond what
we would expect from the permutation null. In fact, there appears there is more
enrichment for low p-values when

To address this limitation, we re-ran the seasonal GLM model
on data where the seasonal labels are randomly permuted.
